\TITLE

### 2020-12-22 response-v3-content.tex

\REVIEW{DONE}{Table 3: tidy the headers.}
  { The headers have been cleaned up and linebreaks were introduced so
    the resizebox of the table presents the table now larger}

\REVIEW{TODO}{Figure 5-6: can be combined to one figure with two
  panels (using ggplot2 and save the space of the labels of the
  horizontal axis).  }
  { todo}

\REVIEW{TODO}{Figure 7-8: can be one figure with two panels; pop
  density 2010 needs to be cleaned.}
  { todo}

\REVIEW{PROGRESS}{Figure 9-14: combine into one figure.}
  {

\todo{the lines are missing in the images showing the NONE line}

First we decided to only disaly the top 10 results of each prediction
with a factor. Second we have included the combined picture of it for
deth and cases in the {\bf Figure Combined}. We can include this
figure in the paper if the editor thinks this figure is better or
sufficient. At this tiem we still have included them in a subfigure
(a) and (b) in the paper as the scales on the y axis are
different. Please let us know what you think and we can adapt this.

\begin{figure}[!h]
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_CasesAndDeath.pdf}

        {\bf Figure Combined} Best predictions for cases over all risk factors.

        %\label{fig:place-top10-joint}

\end{figure}

### 2020-12-31 response-v3-content.tex

\definecolor{PROGRESS}{cmyk}{0.10, 0.10, 0.0, 0.0, 1.00}
\definecolor{TODO}{cmyk}{0.0, 0.10, 0.10, 0.00, 1.00}
\definecolor{DONE}{cmyk}{0.10, 0.0, 0.10, 0.0, 1.0}

\newcommand{\REVIEW}[3]{
  \begin{tcolorbox}[colback={#1}]
    {\bf {#1}. {#2}}
 \end{tcolorbox}
  \begin{quote}
    {#3}
  \end{quote}
}

REVISION DUE: 01.12.2021

\begin{itemize}
\item Manuscript ID JDS2007-001 to Journal of Data Science.

\item \url{http://jds.ruc.edu.cn/EN/column/item8.shtml}

\item \url{http://jds.ruc.edu.cn/EN/column/column3.shtml}

\item Progress: \url{https://www.e-publications.org/ruc/sbs/JDS/}

\end{itemize}

\parindent 0pt We are happy to resubmit our paper and are very thankful for the great reviews we received.

If possible we would like to acknowledge the reviewers by name in the
acknowledgement section, but this depends on them and you.

``AICov: A Deep Learning Framework for COVID-19 Forecastingwith
CovariatesAICov: An Integrative Deep Learning Framework for
COVID-19Forecasting with Covariates''

Manuscript ID JDS2007-001 to Journal of Data Science.

Progress: \url{https://www.e-publications.org/ruc/sbs/JDS/}

@@

  \REVIEW{DONE} {Needs page number (line number) for ease of
    referencing in the review.}
  {Page numbers and line numbers were
    activated with the review style from the new JDS \LaTeX{}
    template}

  \REVIEW{DONE} {Do not italicize in the text.}
  {All italicized text
    have been removed.  Formulas enclosed in dollar signs are in
    italized text as is default for the JDS document style.}

  \REVIEW{DONE} {AICov needs to be defined in the abstract.}
  {We added ``We present the architecture of an artificial
    intelligence enhanced COVID-19 analysis (in short AICov)''
  in the abstract. We also defined COVID-10 in the abstract.}

\REVIEW{DONE}{Acronyms need to be defined at their first occurrences
  (e.g., AI in the intro). An acronyme table is included in table 1,
  we added the following acronyms to the paper}
  {All acronyms have been defined at their first usage. In addition
    we have added a section Acronyms in which all acronyms are listed
    to make it easier for the reader to look them up in case they are
    used later on in the paper. All riskfactors have been capitalized.
    The duplicated Risk factors were removed.
  }

@@

\REVIEW{TODO}{Figure 2: please present the equations as equations. The
  notations used in the equation need a full check (e.g., h is used as
  both the dimension and vector). I'd like to see a clear distinction
  between inputs/outputs and parameters. I'd suggest that the inputs
  be set up before the equations are presented.}
  { todo}

\REVIEW{DONE}{Regenerate the figures into pdf format (the current
  jpg/png figures blur when zoomed in).}
  {All images have been included as PDF images}

@@

\REVIEW{DONE}{Table 2: consider reformating it; it would not fit the
  page width in print.}
  { Table 2 has been reformatted. It was previously fit in the column
    with resize box. While rotating the headers the font is
    increased. The table still fits in the column as it still uses
    resizebox.}

\REVIEW{DONE}{Table 3: tidy the headers.}
  { The headers have been cleaned up and linebreaks were introduced so
    the resizebox of the table presents the table now larger}

\REVIEW{DONE}{Figure 5-6: can be combined to one figure with two
  panels (using ggplot2 and save the space of the labels of the
  horizontal axis).  }
  {The figures were combined as subfigures into Figure \ref{fig:magic-1} (a) and (b)}

\REVIEW{DONE}{Figure 7-8: can be one figure with two panels; pop
  density 2010 needs to be cleaned.}
    {The figures were combined as subfigures into Figure \ref{fig:error-death-popdensity} (a) and (b)}

@@

\REVIEW{PROGRESS}{Figure 9-14: combine into one figure.}
  {

\todo{the lines are missing in the images showing the NONE line}

First we decided to only disaly the top 10 results of each prediction
with a factor. Second we have included the combined picture of it for
deth and cases in the {\bf Figure Combined}. We can include this
figure in the paper if the editor thinks this figure is better or
sufficient. At this tiem we still have included them in a subfigure
(a) and (b) in the paper as the scales on the y axis are
different. Please let us know what you think and we can adapt this.

%\begin{figure}[!h]
{
        \centering
        \includegraphics[width=.9\textwidth]{images/predict/PlaceTop10_CasesAndDeathNEW2.pdf}

        {\bf Figure Combined} Best predictions for cases over all risk factors.
The two vertical lines represent the experiment in which no additional Risk factor is used for training. The top one for deaths and the bottom one for cases.}        
        %\label{fig:place-top10-joint}

%\end{figure}

@@

\REVIEW{DONE}{Section 5.2, paragraph 2 line 6, no need to capitalize for
  the word “Samples”. Line 5 from the bottom, no need to capitalize
  for the word “Insurance”. Please be careful with your writing.
}
{The capitaization has been corrected. The paper has been reviewed by
  2 native English speakers. In addition 2 grammar checking programs
  were used on the entire paper. One of the reviewers serves also as
  editor in other journals.}

\REVIEW{TODO}{Section 5.2, the “order for cases sorted by minimum model
  order” and “order for deaths sorted by minimum model error”
  paragraphs are redundant, as the same information is already
  displayed in the x-legend for Figures 5 and 6.
}
  { todo}

\REVIEW{TODO}{In Table 3, what is the unit for the error terms? The
  errors in Figures 7 and 8 are percentages. If errors in Table 3 are
  also percentages please clearly mark. Also, the numbers in Figures 7
  and 8 do not align with numbers in row 1 of Table 3. Please check
  your numbers with care.
}
  { todo}

\REVIEW{DONE}{Please adjust the location of your figures so they do not
  look pages apart from their interpretations.
}
  {The location have een adjusted, but LaTeX tries to optimize the
  placement. We have used the !h flag to force placement. If this
  placement is still not sufficient please let us know. We also
  removed images in order to facilitatie better placement. The
  document is submitted in drafts mode which also could influence the
  placement. We have tried the document in final mode with the LaTeX
  style and it seems the placement is now fixed as we removed images.}

\REVIEW{DONE}{If I am reading it correctly, Figures 9 and 11 are only
  the “zoom in” versions of partial information from Figure
  13. Similarly for the right column. Why waste space on two more
  figures when you could make Figures 13 and 14 bigger and explain the
  findings?
}
  {We have provided in an earlier comment that we now only include the
  Top 10 instead of Top 1, and Top 5 to fulfull the desire of the
  reviewers to have these images combined. However we still separated
  the deaths from teh cases view to ease the readers ability to see
  more details. HOwever we can easily replace the image with the one
  provided earlier if the reviewers desire. This is a small change and
  will appreciate the revieers feedback on this further.}

### 2020-12-31 vonLaszewski-covid.tex
update response

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% the following edits should be done by Journal typesetters
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{page}{1}            % set the first page number
\jdsmonth{January}              % month
\jdsyear{2021}                  % year
\jdsvolume{xx}                  % volume number
\jdsissue{xx}                   % issue number
\jdsdoi{xx.xxxx/xxxxxxxxx}      % doi
\jdsreceived{???, 2020}       % optional: comment it out if no received date
\jdsaccepted{???, 2021}         % optional: comment it out if no accepted date
%% manually set running header for a shorter list of authors if needed
% \shortauthors{A Author A, et al.}

@@

\begin{requirement}{\bf Ease of Use.}
  A major design criterion for AICov is that the framework must be
  easy to use, and extensions can be made to allow usability of both
  the Application Programming Interfaces (API) as well as the user
  interface. \Solution To address these requirements, we are devising
  a specialized but easy to use time series API for COVID-19 that
  integrates common tasks such as automated filtering and
  normalization of the data.
\end{requirement}

\begin{requirement}{\bf Interactive Access.}
  Due to the experimental nature of analyzing the data, AICov must
  support the exploration of the data in an interactive
  fashion. \Solution As many data scientists use Jupyter Notebooks to
  integrate their work interactively, AICov integrates such
  notebooks. Jupyter notebooks allow rapid modification of the
  analysis workflow through the ease of Python as programming
  language. Additionally, they enable us to formulate easily
  sophisticated scientific analytics workflows with the help of
  Python and Jupyter Notebooks.
\end{requirement}

\begin{requirement}{\bf Expandable API.}
  Assuming that new models and other analysis algorithms will be
  developed over time, AICov must allow the integration of such
  APIs. \Solution To address this requirement, we are developing an
  abstract API for data, analysis, and metadata parameter
  adjustments. External services can be integrated with the help of
  REST (REpresentational State Transfer) services. The REST services
  are automatically generated from function specifications.
\end{requirement}

\begin{requirement}{\bf Flexible Data Source Integration.}
  The integration of various sources of data is a key part of
  AICov. \Solution To achieve this goal, we provide a number of
  abstractions and data manipulation functions to extract needed data
  from established sources. Furthermore, the data can be combined, and
  additional data wrangling by external groups can be integrated.
  Through such abstractions, it is possible to replace, add, and
  correct data sets that are part of the analysis. This allows us to
  compare different results created from different data
  sets. Moreover, we include data selection directly in our framework
  to easily and quickly reuse them in a data mashup. An important
  example is that the data need not be static over the disease's
  progression but can be continuously updated. This also has a
  significant impact on our analytics algorithms.
\end{requirement}

\begin{requirement}{\bf Automated Update of the Analytics.}
  As the data can change, previous analyses may have to be
  updated. \Solution Our forecast is not just a single script but
  includes a mechanism to register multiple workflows of continuously
  integrated (CI) analysis that are automatically rerun when new data
  are made available to the system. Previous results are
  maintained. Metadata with these runs can retrieve the versioned data
  sets used to calculate and store the versioned analytics workflow.
\end{requirement}

\begin{requirement}{\bf Flexible Model definition.}
  We want to allow experimentation with various models in AICov that
  may be easily and flexibly definable as workflows. \Solution We give
  functional abstraction definitions that enables us to define the
  models ourselves or integrate third party models describing the
  spread of the disease.
\end{requirement}

\begin{requirement}{\bf Deep Learning Forecast.}
  As the forecasting models depend on changing data that are made
  available daily, it is important for AICov to utilize the newly
  available data. Many models can be applied to this, including moving
  averages based models or models that are purely derived from deep
  learning. \Solution To address this requirement, AICov allows for
  the integration of both. Furthermore, in our deep learning
  framework, we can integrate an automated search for important risk
  factors, which is the focus of this study.
\end{requirement}

\begin{requirement}{\bf Model Orchestration.}
  To coordinate the different model predictions and the generation of
  the deep learning forecasts, we need the ability to orchestrate them
  while applying a number of parameters. \Solution To address this
  requirement, the AICov architecture includes the ability to
  integrate parameter sweeps to, for example, identify
  hyperparameters, or integrate different data sets as parameters to
  identify suitable forecast models that can deliver the one which
  fits the best.
\end{requirement}

\begin{requirement}{\bf Compute Resource Mapping.}
  For other uses of AICov, we need to integrate a flexible resource
  utilization framework. \Solution To address this requirement, we
  leverage from our earlier work and utilize through Cloudmesh and
  National Institute of Standards and Technology (NIST) Big Data
  Working Group (NBDIF) definitions cloud services into the
  architecture \citep{las-19-nist}. This includes containers but also
  infrastructure services in the cloud. Through these service
  integrations, we also provide access to Graphics Processing Units
  (GPUs).
\end{requirement}

\begin{requirement}{\bf Convenient Interfaces.}
  As we have a wide variety of users, we need to enable interfaces
  that are used by the various communities. \Solution To address this
  requirement, we provide a number of APIs, REST services and make
  them available via Jupyter Notebooks. In addition, we developed some
  custom widgets for the notebooks that are specifically targeted
  towards data integration, parameter manipulation, and visualization
  of the results
\end{requirement}

@@

\begin{question} Can we apply deep learning strategies that self-learn the behavior of a model in order to provide future predictions? See Section \ref{sec:emperical}.
\label{q:1}
\end{question}

\begin{question} Can we use real time data as input and apply deep learning strategies instead of models that self learn and provide future predictions? See Section \ref{sec:lstm-covariate}.
\label{q:2}
\end{question}

\begin{question} Does the inclusion of covariates improve the prediction quality while including geospatial and socio-economic risk factors? See Section \ref{sec:lstm-covariate}.
\label{q:3}
\end{question}

\begin{question} What impact do we see when we introduce many risk factors? See Section \ref{sec:lstm-many}.
\label{q:4}
\end{question}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{images/magic-1.png}

    \begin{subfigure}{.4\textwidth}
      \centering
      % include first image
      % \includegraphics[width=.8\linewidth]{image_file_name}  
      \caption{Prediction acuracy for deaths.}
      \label{fig:magic-a}
    \end{subfigure}
    \begin{subfigure}{.4\textwidth}
      \centering
      % include second image
      %\includegraphics[width=.8\linewidth]{image_file_name}  
      \caption{Prediction acuracy for cases.}
      \label{fig:magic-b}
    \end{subfigure}

@@

\begin{figure}[!h]
  \begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/predict/Length_5-fields_pop_density_2010-Cumulative-Cases.png}
    %\vspace{-1cm}
    \caption{Model prediction error cases.}
    \label{fig:error-case-popdensity}
  \end{subfigure}
  \begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/predict/Length_5-fields_pop_density_2010-Cumulative-Death.png}
    %\vspace{-1cm}
    \caption{Model prediction error deaths.}
    \label{fig:error-death-popdensity}
    \end{subfigure}

@@

%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Cases.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all cases over all risk factors.}
%        \label{fig:place-top5-cases}
%    \end{minipage}
%    \ \
%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Death.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all deaths  over all risk factors.}
%        \label{fig:place-top5-death}
%    \end{minipage}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_CasesNEW.pdf}
        \caption{Cummulative error for cases}
        \label{fig:place-top10-cases}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_DeathNEW.pdf}
        \caption{Cumulatice error for deaths.}
        \label{fig:place-top10-death}
    \end{subfigure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% the following edits should be done by Journal typesetters
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{page}{1}            % set the first page number
\jdsmonth{January}              % month
\jdsyear{2021}                  % year
\jdsvolume{xx}                  % volume number
\jdsissue{xx}                   % issue number
\jdsdoi{xx.xxxx/xxxxxxxxx}      % doi
\jdsreceived{Jun 30, 2020}       % optional: comment it out if no received date
\jdsaccepted{???, 2021}         % optional: comment it out if no accepted date
%% manually set running header for a shorter list of authors if needed
% \shortauthors{A Author A, et al.}

@@

\begin{requirement}{\bf Ease of Use.} \normalfont
  A major design criterion for AICov is that the framework must be
  easy to use, and extensions can be made to allow usability of both
  the Application Programming Interfaces (API) as well as the user
  interface. \Solution To address these requirements, we are devising
  a specialized but easy to use time series API for COVID-19 that
  integrates common tasks such as automated filtering and
  normalization of the data.
\end{requirement}

\begin{requirement}{\bf Interactive Access.} \normalfont
  Due to the experimental nature of analyzing the data, AICov must
  support the exploration of the data in an interactive
  fashion. \Solution As many data scientists use Jupyter Notebooks to
  integrate their work interactively, AICov integrates such
  notebooks. Jupyter notebooks allow rapid modification of the
  analysis workflow through the ease of Python as programming
  language. Additionally, they enable us to formulate easily
  sophisticated scientific analytics workflows with the help of
  Python and Jupyter Notebooks.
\end{requirement}

\begin{requirement}{\bf Expandable API.} \normalfont
  Assuming that new models and other analysis algorithms will be
  developed over time, AICov must allow the integration of such
  APIs. \Solution To address this requirement, we are developing an
  abstract API for data, analysis, and metadata parameter
  adjustments. External services can be integrated with the help of
  REST (REpresentational State Transfer) services. The REST services
  are automatically generated from function specifications.
\end{requirement}

\begin{requirement}{\bf Flexible Data Source Integration.} \normalfont
  The integration of various sources of data is a key part of
  AICov. \Solution To achieve this goal, we provide a number of
  abstractions and data manipulation functions to extract needed data
  from established sources. Furthermore, the data can be combined, and
  additional data wrangling by external groups can be integrated.
  Through such abstractions, it is possible to replace, add, and
  correct data sets that are part of the analysis. This allows us to
  compare different results created from different data
  sets. Moreover, we include data selection directly in our framework
  to easily and quickly reuse them in a data mashup. An important
  example is that the data need not be static over the disease's
  progression but can be continuously updated. This also has a
  significant impact on our analytics algorithms.
\end{requirement}

\begin{requirement}{\bf Automated Update of the Analytics.} \normalfont
  As the data can change, previous analyses may have to be
  updated. \Solution Our forecast is not just a single script but
  includes a mechanism to register multiple workflows of continuously
  integrated (CI) analysis that are automatically rerun when new data
  are made available to the system. Previous results are
  maintained. Metadata with these runs can retrieve the versioned data
  sets used to calculate and store the versioned analytics workflow.
\end{requirement}

\begin{requirement}{\bf Flexible Model definition.} \normalfont
  We want to allow experimentation with various models in AICov that
  may be easily and flexibly definable as workflows. \Solution We give
  functional abstraction definitions that enables us to define the
  models ourselves or integrate third party models describing the
  spread of the disease.
\end{requirement}

\begin{requirement}{\bf Deep Learning Forecast.} \normalfont
  As the forecasting models depend on changing data that are made
  available daily, it is important for AICov to utilize the newly
  available data. Many models can be applied to this, including moving
  averages based models or models that are purely derived from deep
  learning. \Solution To address this requirement, AICov allows for
  the integration of both. Furthermore, in our deep learning
  framework, we can integrate an automated search for important risk
  factors, which is the focus of this study.
\end{requirement}

\begin{requirement}{\bf Model Orchestration.} \normalfont
  To coordinate the different model predictions and the generation of
  the deep learning forecasts, we need the ability to orchestrate them
  while applying a number of parameters. \Solution To address this
  requirement, the AICov architecture includes the ability to
  integrate parameter sweeps to, for example, identify
  hyperparameters, or integrate different data sets as parameters to
  identify suitable forecast models that can deliver the one which
  fits the best.
\end{requirement}

\begin{requirement}{\bf Compute Resource Mapping.} \normalfont
  For other uses of AICov, we need to integrate a flexible resource
  utilization framework. \Solution To address this requirement, we
  leverage from our earlier work and utilize through Cloudmesh and
  National Institute of Standards and Technology (NIST) Big Data
  Working Group (NBDIF) definitions cloud services into the
  architecture \citep{las-19-nist}. This includes containers but also
  infrastructure services in the cloud. Through these service
  integrations, we also provide access to Graphics Processing Units
  (GPUs).
\end{requirement}

\begin{requirement}{\bf Convenient Interfaces.} \normalfont
  As we have a wide variety of users, we need to enable interfaces
  that are used by the various communities. \Solution To address this
  requirement, we provide a number of APIs, REST services and make
  them available via Jupyter Notebooks. In addition, we developed some
  custom widgets for the notebooks that are specifically targeted
  towards data integration, parameter manipulation, and visualization
  of the results
\end{requirement}

@@

\begin{question} \normalfont Can we apply deep learning strategies that self-learn the behavior of a model in order to provide future predictions? See Section \ref{sec:emperical}.
\label{q:1}
\end{question}

\begin{question} \normalfont Can we use real time data as input and apply deep learning strategies instead of models that self learn and provide future predictions? See Section \ref{sec:lstm-covariate}.
\label{q:2}
\end{question}

\begin{question} \normalfont Does the inclusion of covariates improve the prediction quality while including geospatial and socio-economic risk factors? See Section \ref{sec:lstm-covariate}.
\label{q:3}
\end{question}

\begin{question} \normalfont What impact do we see when we introduce many risk factors? See Section \ref{sec:lstm-many}.
\label{q:4}
\end{question}

@@

\begin{figure}[!h]
    \centering

    \begin{subfigure}{.49\textwidth}
      \centering
      \includegraphics[width=1.0\linewidth]{images/predict/Fig4a.pdf}  
      \caption{Prediction acuracy for deaths.}
      \label{fig:magic-a}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
      \centering
      \includegraphics[width=1.0\linewidth]{images/predict/Fig4b.pdf}        
      \caption{Prediction acuracy for cases.}
      \label{fig:magic-b}
    \end{subfigure}

@@

\begin{figure}[!h]
  \begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/predict/Length_5-fields_pop_density_2010-Cumulative-Cases.pdf}
    %\vspace{-1cm}
    \caption{Model prediction error cases.}
    \label{fig:error-case-popdensity}
  \end{subfigure}
  \begin{subfigure}{.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{images/predict/Length_5-fields_pop_density_2010-Cumulative-Death.pdf}
    %\vspace{-1cm}
    \caption{Model prediction error deaths.}
    \label{fig:error-death-popdensity}
    \end{subfigure}

@@

%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Cases.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all cases over all risk factors.}
%        \label{fig:place-top5-cases}
%    \end{minipage}
%    \ \
%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Death.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all deaths  over all risk factors.}
%        \label{fig:place-top5-death}
%    \end{minipage}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_Cases.pdf}
        \caption{Cummulative error for cases}
        \label{fig:place-top10-cases}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_Death.pdf}
        \caption{Cumulatice error for deaths.}
        \label{fig:place-top10-death}
    \end{subfigure}
